---
title: "Austen & Griffiths (2021) analyses (e.g., RI-CLPMs)"
output: html_notebook
---


```{r}

library(lavaan)
library(dplyr)
library(lubridate)
library(anytime)
library(tidyverse)
library(gghalves)
library(psych)
library(car)
library(ggpubr)
```


#load merged file 
```{r}
merged <- read.csv("Final_merged_clean.csv")
```

#data screening 

##attrition/completers versus non-completers

```{r attrition completers}

#first, assign 0 to NAs so that 1 = complete, 0 = not complete 

merged$Wave_1_complete[is.na(merged$Wave_1_complete)] <- 0
merged$Wave_2_complete[is.na(merged$Wave_2_complete)] <- 0
merged$Wave_3_complete[is.na(merged$Wave_3_complete)] <- 0
merged$Wave_4_complete[is.na(merged$Wave_4_complete)] <- 0


merged$Wave_1_complete <- factor(merged$Wave_1_complete,
levels = c(0, 1),
labels = c("W1 non-completer", "W1 completer"))

merged$Wave_2_complete <- factor(merged$Wave_2_complete,
levels = c(0, 1),
labels = c("W2 non-completer", "W2 completer"))

merged$Wave_3_complete <- factor(merged$Wave_3_complete,
levels = c(0, 1),
labels = c("W3 non-completer", "W3 completer"))


merged$Wave_4_complete <- factor(merged$Wave_4_complete,
levels = c(0, 1),
labels = c("W4 non-completer", "W4 completer"))

```

- wave 1 (completers n = 4859)
- wave 2 (n = 2279)
- wave 3 (n = 1944)
- wave 4 (n = 1737)


```{r attrition analyses}

table(merged$Wave_1_complete)
table(merged$Wave_2_complete)
table(merged$Wave_3_complete)
table(merged$Wave_4_complete)

#contingency tables to look at if there are people who completed W3 but not W2, etc 

mytable <- xtabs(~ Wave_2_complete+Wave_3_complete+Wave_4_complete, data=merged)

ftable(mytable) 

```

- contingency table tells us that there are n = 1886 participants who enrolled for W2 onward, but never ended up participating. We will exclude these participants


```{r remove unusual StartDate_T3 values}
library(naniar)

merged <- merged %>% 
  replace_with_na(replace = list(StartDate_T3 = c(18307, 18308, 18309, 18310, 18321, 18342, 18420)))


```

```{r removing participants who did not participate in wave 2 onward}

merged <- merged %>%  
  dplyr::mutate(participated_at_all = case_when(Wave_2_complete == "W2 non-completer" & Wave_3_complete == "W3 non-completer" 
                                                & Wave_4_complete == "W4 non-completer" ~ 0,
                                      Wave_2_complete == "W2 completer" | Wave_3_complete == "W3 completer" | Wave_4_complete == "W4 completer" ~ 1))

table(merged$participated_at_all) #check that it worked - this is accurate, as it matches results earlier that 1886 people did not participate at all 




merged_final <- merged %>%  #filtering to people who participated 
  filter(participated_at_all == 1)


```



```{r looking at sample sizes from updated dataset}
table(merged_final$Wave_1_complete)
table(merged_final$Wave_2_complete)
table(merged_final$Wave_3_complete)
table(merged_final$Wave_4_complete)



mytable <- xtabs(~ Wave_2_complete+Wave_3_complete+Wave_4_complete, data=merged_final)

ftable(mytable) 
```

```{r filter out <18 yos}

merged_final <- merged_final %>%
  filter(is.na(Age_T2) | (Age_T2 >= 18))

```

```{r calculate var for drop out versus completed all}

merged_final <- merged_final %>%  #here, 1 = anyone who has dropped out at least once, and 0  = anyone who completed every single wave 
  mutate(dropout_at_all = case_when(Wave_2_complete == "W2 non-completer" | Wave_3_complete == "W3 non-completer" 
                                    | Wave_4_complete == "W4 non-completer" ~ 1, 
                                    Wave_2_complete == "W2 completer" & Wave_3_complete == "W3 completer" & 
                                      Wave_4_complete == "W4 completer" ~ 0))

table(merged_final$dropout_at_all)
```


###Experiences by BMI graph 

```{r exp by BMI graph }


p <- merged_final %>% 
  ggplot(aes(x = BMI_T2, y = EDS_bodyweight_MEAN_T2)) +
           geom_smooth() + 
  labs(x = "BMI T1", y = "Experiences of weight discrimination T1") +
  theme_classic()


p2 <- merged_final %>% 
  ggplot(aes(x = BMI_T2, y = WBIS_M_MEAN_T2)) +
           geom_smooth() + 
  labs(x = "BMI T1", y = "Internalised weight bias T1") +
  theme_classic()


#ggsave("EDS by BMI.tiff", plot = p, dpi = 400)

#ggsave("WBIS by BMI.tiff", plot = p2, dpi = 400)

```


##distribution of variables 

###gap between waves 

- date vars: in T3, some dates are unusual values (e.g., 18307) 
    - can back-calculate thees values by subtracting Duration from EndDate? -- for now, have coded these as NA. 
    
    
- the MEDIAN gap between T1 and T2 (i.e., t2 and t3 on gbw) was 183
- the MEDIAN gap between T2 and T3 (i.e., t3 and t4) was 183

```{r gaps between waves}

library(ggridges)


merged_final <- merged_final %>% 
  mutate(StartDate_T2 = anydate(StartDate_T2),
         StartDate_T3 = anydate(StartDate_T3),
         StartDate_T4 = anydate(StartDate_T4)) %>% 
  mutate(gap_T2_T3 = as.numeric(difftime(StartDate_T3, StartDate_T2, unit = "days")),
         gap_T3_T4 = as.numeric(difftime(StartDate_T4, StartDate_T3, unit = "days")))


#descriptives
merged_final %>% 
  select(starts_with("gap")) %>% 
  describe()


#plotting
gap <- merged_final %>% 
  select(starts_with("gap")) %>% 
  pivot_longer(starts_with("gap"), names_to = "Timepoints", values_to = "Gap_in_days") 

#density plot
gap_plot <- gap %>% 
  mutate(Timepoints_labels = case_when(Timepoints == "gap_T3_T4" ~ "T2 to T3", 
                                       Timepoints == "gap_T2_T3" ~ "T1 to T2")) %>% 
  ggplot(aes(x = Gap_in_days, y = Timepoints_labels, fill = Timepoints_labels)) +
  geom_density_ridges() + 
  labs(x = "Gap (in days)", y = "Timepoints") + 
  guides(fill = FALSE)+ 
  theme_classic()


#boxplot
gap_plot_2 <- gap %>% 
  mutate(Timepoints_labels = case_when(Timepoints == "gap_T3_T4" ~ "T2 to T3", 
                                       Timepoints == "gap_T2_T3" ~ "T1 to T2")) %>% 
  ggplot(aes(x = Gap_in_days, y = Timepoints_labels, fill = Timepoints_labels)) +
  geom_boxplot() + 
  labs(x = "Gap (in days)", y = "Timepoints") + 
  guides(fill = FALSE)+ 
  theme_classic()



#ggsave("gap_between_waves.tiff", plot = gap_plot, dpi = 400)

```
  
##distribution of model variables 
```{r}

EDS_distribution <- merged_final %>% 
  select(starts_with(c("EDS"))) %>%  
        pivot_longer(cols = starts_with("EDS"), names_to = "timepoint", values_to = "value") %>% 
        ggplot(aes(timepoint, value)) +
  geom_half_point(side = "l", size = 0.05, alpha = 0.5) + #use points on the other half of the plot 
  geom_half_boxplot(aes(color = timepoint), side = "l", width = 0.5, alpha = 0.3, nudge = 0.1, outlier.shape = NA, 
                    size = 0.75) + #assign the boxplot to the left of the halfplot 
  geom_half_violin(aes(fill = timepoint), side = "r") + 
                     guides(fill = FALSE, color = FALSE) +
                     coord_flip() +
  labs(title = "Experiences of Weight Discrimination (EDS)") + 
                    scale_x_discrete(labels=c("T2", "T3", "T4")) +
                    theme_classic() +
                    theme(axis.title.x = element_blank())
  


WBIS_distribution <- merged_final %>% 
  select(starts_with(c("WBIS"))) %>%  
        pivot_longer(cols = starts_with("WBIS"), names_to = "timepoint", values_to = "value") %>% 
        ggplot(aes(timepoint, value)) +
  geom_half_point(side = "l", size = 0.05, alpha = 0.5) + #use points on the other half of the plot 
  geom_half_boxplot(aes(color = timepoint), side = "l", width = 0.5, alpha = 0.3, nudge = 0.1, outlier.shape = NA,
                    size = 0.75) + #assign the boxplot to the left of the halfplot 
  geom_half_violin(aes(fill = timepoint), side = "r") + 
                     guides(fill = FALSE, color = FALSE) +
                     coord_flip() +
                    labs(title = "Internalized Weight Bias (WBIS-M)") + 
                    scale_x_discrete(labels=c("T2", "T3", "T4")) +
                    theme_classic() +
                    theme(axis.title.x = element_blank())
  



BMI_distribution <- merged_final %>% 
  select(starts_with(c("BMI"))) %>%  
        pivot_longer(cols = starts_with("BMI"), names_to = "timepoint", values_to = "value") %>% 
        ggplot(aes(timepoint, value)) +
  geom_half_point(side = "l", size = 0.05, alpha = 0.5) + #use points on the other half of the plot 
  geom_half_boxplot(aes(color = timepoint), side = "l", width = 0.5, alpha = 0.3, nudge = 0.1, outlier.shape = NA,
                    size = 0.75) + #assign the boxplot to the left of the halfplot 
  geom_half_violin(aes(fill = timepoint), side = "r") + 
                     guides(fill = FALSE, color = FALSE) +
                     coord_flip() +
                    labs(title = "BMI") + 
                    scale_x_discrete(labels=c("TI", "T2", "T3", "T4")) +
                    theme_classic() +
                    theme(axis.title.x = element_blank())
  



Age_distribution <- merged_final %>% 
  select(starts_with(c("Age"))) %>%  
        pivot_longer(cols = starts_with("Age"), names_to = "timepoint", values_to = "value") %>% 
        ggplot(aes(timepoint, value)) +
  geom_half_point(side = "l", size = 0.05, alpha = 0.5) + #use points on the other half of the plot 
  geom_half_boxplot(aes(color = timepoint), side = "l", width = 0.5, alpha = 0.3, nudge = 0.1, outlier.shape = NA,
                    size = 0.75) + #assign the boxplot to the left of the halfplot 
  geom_half_violin(aes(fill = timepoint), side = "r") + 
                     guides(fill = FALSE, color = FALSE) +
                     coord_flip() +
                    labs(title = "Age") + 
                    scale_x_discrete(labels=c("T1", "T2", "T3", "T4")) +
                    theme_classic() +
                    theme(axis.title.x = element_blank())


distributions <- ggarrange(
  BMI_distribution,
  Age_distribution,
EDS_distribution,
WBIS_distribution,
BD_distribution,
WeightBias_distribution, ncol = 2, nrow = 3)


ggsave("var_distributions.tiff", plot = distributions, dpi = 400, height = 12, width = 16, units = "in")

```



##correlation plots

```{r corr plots}

correlations <- merged_final %>% 
  select(BMI_T2, BMI_T3, BMI_T4, SES_T2, SES_T3, SES_T4, starts_with(c("Age", "EDS", "WBIS", "AQoL_MSD_MEAN"))) %>% 
  cor(use = "pairwise.complete.obs") #need to specify complete.obs so that R knows what to do with the missing data 

correlations[lower.tri(correlations)] <- NA #remove the redundant lower half of the triangle


correlations_long <- correlations %>%  #turn into long format so we can plot
  as.data.frame() %>%  
  rownames_to_column("measure2") %>% 
  pivot_longer(cols = -measure2,
             names_to = "measure1", 
             values_to = "cor") %>% 
  mutate(nice_cor = round(cor, 2)) %>% 
  filter(measure2 != measure1) %>% 
  filter(!is.na(cor)) %>% 
   mutate(measure1 = fct_inorder(measure1),
         measure2 = fct_inorder(measure2))

heatmap_correlations <- ggplot(correlations_long, 
       aes(x = measure2, y = measure1, fill = cor)) +
  geom_tile() +
  geom_text(aes(label = nice_cor), color = "white", size = 2.5) +
  scale_fill_viridis(option = "plasma", limits = c(-1, 1), direction = -1) +
  labs(x = NULL, y = NULL) +
  coord_equal() +
  theme_classic() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(angle = 45, color = "black", hjust = 1),
        axis.text.y = element_text(color = "black")) +
  scale_x_discrete(labels = c("BMI T1", "BMI T2", "BMI T3", "SES T1", "SES T2", "SES T3", "Age T1", "Age T2", "Age T3", 
                              "Experiences T1", "Experiences T2", 
                              "Experiences T3", "Internalized T1",
                              "Internalized T2", "Internalized T3", "Psychological QoL T1",
                              "Psych QoL T2", "Psych QoL T3")) +
  scale_y_discrete(labels = c("BMI T2", "BMI T3", "SES T1", "SES T2", "SES T3",
                              "Age T1", "Age T2", "Age T3", "Experiences T1", 
                              "Experiences T2", "Experiences T3", "Internalized T1", "Internalized T2", "Internalized T3",
                              "Psych QoL T1", "Psych QoL T2", "Psych QoL T3"))
  



heatmap_correlations

point_correlations <- ggplot(correlations_long, 
       aes(x = measure2, y = measure1, color = cor)) +
  # Size by the absolute value so that -0.7 and 0.7 are the same size
  geom_point(aes(size = abs(cor))) +
  scale_color_gradient2(low = "#E16462", mid = "white", high = "#0D0887",
                        limits = c(-1, 1)) +
  scale_size_area(max_size = 15, limits = c(-1, 1), guide = FALSE) +
  labs(x = NULL, y = NULL) +
  coord_equal() +
  theme_minimal() +
  theme(panel.grid = element_blank(), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

point_correlations

#ggsave("point_correlations.tiff", plot = point_correlations, dpi = 400, height = 12, width = 12, units = "in")

#ggsave("heatmap_correlations.tiff", plot = heatmap_correlations, dpi = 400)



```

#Descriptive statistcis for model variables 

```{r descriptives table}

descriptives <- merged_final %>% 
  dplyr::select(starts_with(c("WBIS", "EDS", "BMI", "SES", "Age", "Duration", "AQoL")))



descriptives_table <- format(stat.desc(descriptives), scientific = FALSE, digits = 1)
#stat.desc function gives scientific notation as default output, so we want to turn that off 
#digits = 1 gives us all the values to two dp 
view(descriptives_table)

```

##country of residence

- 0 = prefer not to say
- 1 = Australia
- 2 = Canada
- 3 = United Kingdom
- 4 = USA
- 5 = somewhere else


```{r}
merged_final %>% 
  select(Country_T1) %>% 
  table()

```

##start and end dates 
```{r}
merged_final %>% 
  select(starts_with(c("Start", "End"))) %>% 
  view()

```

##sex identity, attraction, and experiences
```{r}

sex <- merged_final %>% 
  select(Sex_identity_T1, Sex_attraction_T1, Sex_experiences_T1) %>% 
  mutate(Sex_identity_T1 = as.factor(Sex_identity_T1),
         Sex_attraction_T1 = as.factor(Sex_attraction_T1), 
         Sex_experiences_T1 = as.factor(Sex_experiences_T1))


sex %>% 
  select(Sex_identity_T1) %>% 
  table()


sex %>% 
  select(Sex_attraction_T1) %>% 
  table()

sex %>% 
  select(Sex_experiences_T1) %>% 
  table()
```
##gender

```{r}


merged_final %>% #how many participants identify as cis-gender male versus another identity
  select(Gender_T1) %>% 
  table()
```

```{r}

gender <- merged_final %>%    #selecting participants who identified as a gender identity other than cis-gender male 
  select(starts_with("Gender_list")) %>% 
  mutate_all(as.numeric) %>% 
  mutate(gender_sum = rowSums(select(., Gender_list_0:Gender_list_38), na.rm = TRUE)) %>% 
  
gs <- gender %>%  #of the above participants, select those participants who listed one gender identity 
  filter(gender_sum == 1) 

gs %>% 
  colSums(na.rm = TRUE) #of those who listed just one identity, find frequency for each gender identity option 

  gm <- gender %>%   #get how many people identified with more than one gender
  select(gender_sum) %>% 
  filter(gender_sum >= 2)
  
  

```

##race 

- We have race data for 647 participants due to a server-side error in data collection 
  - Asian: n = 23 (4%)
  - Black: n = 62 (10%)
  - Hispanic: n = 51 (8%)
  - White: n = 402 (62%)
  - Other racial identity: n = 19 (2%)
  - Multi-racial identity: n = 99 (15%)
```{r race freqs}

#making a table with descriptives for the race variables, which were calculated in SPSS
race_descriptives <- merged_final %>% 
  select(starts_with("Race")) %>% 
  describe()


#work out percentages
race_descriptives %>%  
  select (n) %>% 
  mutate(prop = (n/647))


#participated_at_all
merged_final <- merged_final %>%  
  dplyr::mutate(participated_at_all = case_when(Wave_2_complete == "W2 non-completer" & Wave_3_complete == "W3 non-completer" 
                                                & Wave_4_complete == "W4 non-completer" ~ 0,
                                      Wave_2_complete == "W2 completer" | Wave_3_complete == "W3 completer" | Wave_4_complete == "W4 completer" ~ 1))




#make race variables into dummies for regression 


merged_final$Race_Asian[is.na(merged_final$Race_Asian)] <- 0
merged_final$Race_Hispanic[is.na(merged_final$Race_Hispanic)] <- 0
merged_final$Race_White[is.na(merged_final$Race_White)] <- 0
merged_final$Race_Other[is.na(merged_final$Race_Other)] <- 0
merged_final$Race_Black[is.na(merged_final$Race_Black)] <- 0
merged_final$Race_multi[is.na(merged_final$Race_multi)] <- 0


```


###analyses comparing demographics for completers, samples
- logistic regression
  - outcome: dropout_at_all (1 = yes (n = 1901), 0 = no (i.e., completed all waves; n = 1072))
  - IVs = demographic variables @ T2
    - EDS 
    - IWB
    - BMI
    - Age
    - Race - all dummy-coded variables 
    
    
 - for every unit increase in age, the odds of dropping out at all (versus completing all waves) DECREASES by 0.02/a factor of 0.98 (odds ratio)
- for every unit increase in experiences of weight discrimination, the odds of dropping out at all (versus completing all waves) INCREASES by 0.22 /a factor of 1.24 (odds ratio)
- for every unit increase in internalized weight bias, the odds of dropping out at all (versus completing all waves) DECREASES by 0.09 /a factor of 0.91 (odds ratio)
- odds of dropping out not significantly predicted by BMI, psychological quality of life, or race 

```{r logistic regression}
library(aod)
library(ggplot2)

#dropout_at_all: a positive regression coefficient here would indicate that a unit increase in X increases log odds of dropping out at all by X, versus completing all waves


mylogit <- 
  glm(dropout_at_all ~ Likelihood_T1 + BMI_T2 + Age_T2 + EDS_bodyweight_MEAN_T2 + WBIS_M_MEAN_T2 + AQoL_MSD_MEAN_T2 + Race_Asian +
        Race_Hispanic + Race_White + Race_Other + Race_Black + Race_multi, data = merged_final, family = "binomial")

summary(mylogit)


#calculating odds ratios: for every unit increase in X, the odds of dropping out at all (versus completing all waves) increases by a factor of [ODDS RATIO VALUE]

exp(coef(mylogit))
exp(cbind(OR = coef(mylogit), confint(mylogit)))
```

##anovas comparing characteristics of timepoint samples 
```{r}
#experiences of weight discriminatino
# Compute the analysis of variance
y3_eds <- y3_eds %>% 
  mutate(Wave = as.factor(Wave))
res.aov.eds <- aov(EDS_bodyweight_MEAN_T2 ~ Wave, data = y3_eds)
# Summary of the analysis
summary(res.aov.eds)

#internalized weight bias
y3_wbis <- y3_wbis %>% 
  mutate(Wave = as.factor(Wave))
res.aov.wbis <- aov(WBIS_M_MEAN_T2 ~ Wave, data = y3_wbis)
summary(res.aov.wbis)

#psych qol 
y3_aqol <- y3_aqol %>% 
  mutate(Wave = as.factor(Wave))
res.aov.aqol <- aov(AQoL_MSD_TOTAL_T2 ~ Wave, data = y3_aqol)
summary(res.aov.aqol)

#age
y3_age <- y3_age %>%
  mutate(Wave = as.factor(Wave))
res.aov.age <- aov(Age_T2 ~ Wave, data = y3_age)
summary(res.aov.age)
TukeyHSD(res.aov.age) #results are sig. so run Tukey's posthoc comparisons

#ses
y3_ses <- y3_ses %>% 
  mutate(Wave = as.factor(Wave))
res.aov.ses <- aov(SES_T2 ~ Wave, data = y3_ses)
summary(res.aov.ses)
TukeyHSD(res.aov.ses)

#BMI
y3_bmi <- y3_bmi %>% 
  mutate(Wave = as.factor(Wave))
res.aov.bmi <- aov(BMI_T2 ~ Wave, data = y3_bmi)
summary(res.aov.bmi)


```

#standardise variables for RI-CLPMs
- here, I've calculated standardized variables for all of the variables going into our RI-CLPMs. This means that we can get a 95% CI around all of our standardized coefficients, as all of the output is standardized as a result of this. 

```{r standardise}

merged_final <- merged_final %>% 
  mutate(ZWBIS_M_T2 = (WBIS_M_MEAN_T2 - mean(WBIS_M_MEAN_T2, na.rm = TRUE))/sd(WBIS_M_MEAN_T2, na.rm = TRUE),
         ZWBIS_M_T3 = (WBIS_M_MEAN_T3 - mean(WBIS_M_MEAN_T3, na.rm = TRUE))/sd(WBIS_M_MEAN_T3, na.rm = TRUE),
         ZWBIS_M_T4 = (WBIS_M_MEAN_T4 - mean(WBIS_M_MEAN_T4, na.rm = TRUE))/sd(WBIS_M_MEAN_T4, na.rm = TRUE),
         ZBMI_T2 = (BMI_T2 - mean(BMI_T2, na.rm = TRUE))/sd(BMI_T2, na.rm = TRUE),
         ZBMI_T3 = (BMI_T3 - mean(BMI_T3, na.rm = TRUE))/sd(BMI_T3, na.rm = TRUE),
         ZBMI_T4 = (BMI_T4 - mean(BMI_T4, na.rm = TRUE))/sd(BMI_T4, na.rm = TRUE),
         ZEDS_T2 = (EDS_bodyweight_MEAN_T2 - mean(EDS_bodyweight_MEAN_T2, na.rm = TRUE))/sd(EDS_bodyweight_MEAN_T2, na.rm = TRUE),
         ZEDS_T3 = (EDS_bodyweight_MEAN_T3 - mean(EDS_bodyweight_MEAN_T3, na.rm = TRUE))/sd(EDS_bodyweight_MEAN_T3, na.rm = TRUE),
         ZEDS_T4 = (EDS_bodyweight_MEAN_T4 - mean(EDS_bodyweight_MEAN_T4, na.rm = TRUE))/sd(EDS_bodyweight_MEAN_T4, na.rm = TRUE),
         ZAQoL_T2 = (AQoL_MSD_TOTAL_T2 - mean(AQoL_MSD_TOTAL_T2, na.rm = TRUE))/sd(AQoL_MSD_TOTAL_T2, na.rm = TRUE),
         ZAQoL_T3 = (AQoL_MSD_TOTAL_T3 - mean(AQoL_MSD_TOTAL_T3, na.rm = TRUE))/sd(AQoL_MSD_TOTAL_T3, na.rm = TRUE),
         ZAQoL_T4 = (AQoL_MSD_TOTAL_T4 - mean(AQoL_MSD_TOTAL_T4, na.rm = TRUE))/sd(AQoL_MSD_TOTAL_T4, na.rm = TRUE))


```
#RI-CLPMs - constrained with standardised variables 
- running models with standardised variables so we can get 95% CIs around the standardised coefficients - i.e., since we have already standardised them, then the default reg coefficients will all be standardised, 

```{r EDS WBIS RICLPM constrained Z, eval = F}

RICLPM_1z <- '
  # Create between components (random intercepts)
  RIx =~ 1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*ZWBIS_M_T2 + 1*ZWBIS_M_T3 + 1*ZWBIS_M_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZWBIS_M_T2
  wy3 =~ 1*ZWBIS_M_T3
  wy4 =~ 1*ZWBIS_M_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1z.fit <- lavaan(RICLPM_1z, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.1z.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```



```{r WBIS AQoL constrained Z, eval = F}

RICLPM.4z <- '
  # Create between components (random intercepts)
  RIx =~1*1*ZWBIS_M_T2 + 1*1*ZWBIS_M_T3 + 1*1*ZWBIS_M_T4
  RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*1*ZWBIS_M_T2
  wx3 =~ 1*1*ZWBIS_M_T3
  wx4 =~ 1*1*ZWBIS_M_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.4z.fit <- lavaan(RICLPM.4z, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.4z.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r WBIS BMI constrained Z, eval = F}

RICLPM.5z <- '
  # Create between components (random intercepts)
  RIx =~1*1*ZWBIS_M_T2 + 1*1*ZWBIS_M_T3 + 1*1*ZWBIS_M_T4
  RIy =~ 1*ZBMI_T2 + 1*ZBMI_T3 + 1*ZBMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*1*ZWBIS_M_T2
  wx3 =~ 1*1*ZWBIS_M_T3
  wx4 =~ 1*1*ZWBIS_M_T4
  
  wy2 =~ 1*ZBMI_T2
  wy3 =~ 1*ZBMI_T3
  wy4 =~ 1*ZBMI_T4
  
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5z.fit <- lavaan(RICLPM.5z, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.5z.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r EDS AQoL constrained Z, eval = F}

RICLPM_3z <- '
  # Create between components (random intercepts)
  RIx =~1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4
  RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.3z.fit <- lavaan(RICLPM_3z, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.3z.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r BMI EDS constrained Z, eval = F}

RICLPM_2z <- '
  # Create between components (random intercepts)
  RIx =~1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4
  RIy =~ 1*ZBMI_T2 + 1*ZBMI_T3 + 1*ZBMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZBMI_T2
  wy3 =~ 1*ZBMI_T3
  wy4 =~ 1*ZBMI_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2z.fit <- lavaan(RICLPM_2z, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2z.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```


#RI-CLPMs - non-standardised 


- '=~': use when defining a latent variable (e.g., random intercepts and within-person centred vars)
- '~': regressed on - use when defining lagged effects. 
- Pre-multiply (*) components with the same label to constrain them to the same value  

- int.ov.free: if FALSE, the intercepts of the observed vars (i.e., group means?) are fixed to zero. if TRUE, free to vary (Hamaker et al., 2015 suggest making group means free to vary over time and if this doesn't work, need to investigate source of misfit. If fine, then proceed)


##EDS <-> WBIS
- throughout, we have some code looking at RI-CLPMs by BMI category. However, these analyses are likely under-powered in our sample. Readers may consult this code out of interest re: how to constrain cross-lagged and auto-regressive parameters to be equal within groups over time in the Lavaan code 

```{r EDS WBIS unconstrained, eval = F}

RICLPM_1a <- '
  # Create between components (random intercepts)
  RIx =~ 1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*WBIS_M_MEAN_T2+ 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ wx2 + wy2
  wy3 ~ wx2 + wy2       
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1a.fit <- lavaan(RICLPM_1a, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.1a.fit, standardized = T, fit.measures = TRUE)
```


```{r EDS WBIS RICLPM constrained, eval = F}

RICLPM_1b <- '
  # Create between components (random intercepts)
  RIx =~ 1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*WBIS_M_MEAN_T2+ 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1b.fit <- lavaan(RICLPM_1b, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.1b.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.1a.fit, RICLPM.1b.fit)
```
- We estimate the traditional CLPM by setting the variance and covariance of the random intercepts to 0 
- Chi square test & interpreting the AIC and BIC values suggests that the traditional CLPM fits significantly worse than the RI-CLPM (p < .001)

```{r EDS WBIS CLPM, eval = F}

CLPM_1 <- '
  # Create between components (random intercepts)
  RIx =~ 1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*WBIS_M_MEAN_T2+ 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2       
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ 0*RIx    #variance
  RIy ~~ 0*RIy
  RIx ~~ 0*RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
CLPM.1.fit <- lavaan(CLPM_1, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(CLPM.1.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.1a.fit, CLPM.1.fit)

```



```{r EDS WBIS RICLPM constrained by BMI, eval = F}

RICLPM_1c <- '
  # Create between components (random intercepts)
  RIx =~ 1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*WBIS_M_MEAN_T2+ 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ c(a1, a2, a3)*wx2 + c(b1, b2, b3)*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c(c1, c2, c3)*wx2 + c(d1, d2, d3)*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ c(a1, a2, a3)*wx3 + c(b1, b2, b3)*wy3
  wy4 ~ c(c1, c2, c3)*wx3 + c(d1, d2, d3)*wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1c.fit <- lavaan(RICLPM_1c, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T, group = "BMI_T2_categories") 
summary(RICLPM.1c.fit, standardized = T, fit.measures = TRUE)

```
##BMI <-> Internalised weight bias

```{r BMI WBIS UNCONSTRAINED, eval = F}

RICLPM.5a <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

   # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5a.fit <- lavaan(RICLPM.5a, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.5a.fit, standardized = T, fit.measures = TRUE)


```


```{r BMI WBIS CONSTRAINED, eval = F}

RICLPM.5b <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

   # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5b.fit <- lavaan(RICLPM.5b, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.5b.fit, standardized = T, fit.measures = TRUE)

anova(RICLPM.5a.fit, RICLPM.5b.fit)
```

```{r BMI WBIS CLPM, eval = F}

CLPM_5 <- '
   # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2       
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ 0*RIx    #variance
  RIy ~~ 0*RIy
  RIx ~~ 0*RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
CLPM.5.fit <- lavaan(CLPM_5, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(CLPM.5.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.5a.fit, CLPM.5.fit)

```


```{r BMI WBIS CONSTRAINED by BMI, eval = F}

RICLPM.5c <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

   # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ c(a1, a2, a3)*wx2 + c(b1, b2, b3)*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c(c1, c2, c3)*wx2 + c(d1, d2, d3)*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ c(a1, a2, a3)*wx3 + c(b1, b2, b3)*wy3
  wy4 ~ c(c1, c2, c3)*wx3 + c(d1, d2, d3)*wy3

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5c.fit <- lavaan(RICLPM.5c, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T, group = "BMI_T2_categories") 
summary(RICLPM.5c.fit, standardized = T, fit.measures = TRUE)

```






##BMI <-> EDS

```{r BMI EDS unconstrained, eval = F}

RICLPM_2a <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2a.fit <- lavaan(RICLPM_2a, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2a.fit, standardized = T, fit.measures = TRUE)


```


```{r BMI EDS constrained, eval = F}

RICLPM_2b <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2b.fit <- lavaan(RICLPM_2b, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2b.fit, standardized = T, fit.measures = TRUE)

anova(RICLPM.2a.fit, RICLPM.2b.fit) #compare fit of constrained and unconstrained
```


```{r BMI EDS CLPM, eval = F}

CLPM_2 <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ 0*RIx
  RIy ~~ 0*RIy
  RIx ~~ 0*RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
CLPM.2.fit <- lavaan(CLPM_2, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2a.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.2a.fit, CLPM.2.fit)
```

```{r BMI EDS constrained by BMI - supplementary, eval = F}

RICLPM_2c <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ c(a1, a2, a3)*wx2 + c(b1, b2, b3)*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c(c1, c2, c3)*wx2 + c(d1, d2, d3)*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ c(a1, a2, a3)*wx3 + c(b1, b2, b3)*wy3
  wy4 ~ c(c1, c2, c3)*wx3 + c(d1, d2, d3)*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2c.fit <- lavaan(RICLPM_2c, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T, group = "BMI_T2_categories") 
summary(RICLPM.2c.fit, standardized = T, fit.measures = TRUE)

```



#EDS <-> AQoL 

```{r EDS AQoL unconstrained, eval = F}

RICLPM_3a <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.3a.fit <- lavaan(RICLPM_3a, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.3a.fit, standardized = T, fit.measures = TRUE)


```


```{r EDS AQoL constrained, eval = F}

RICLPM_3b <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.3b.fit <- lavaan(RICLPM_3b, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.3b.fit, standardized = T, fit.measures = TRUE)

anova(RICLPM.3a.fit, RICLPM.3b.fit) #compare the fit of the constrained and unconstrained models

```


```{r EDS AQoL CLPM, eval = F}

CLPM_3 <- '
  # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ 0*RIx
  RIy ~~ 0*RIy
  RIx ~~ 0*RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
CLPM.3.fit <- lavaan(CLPM_3, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(CLPM.3.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.3a.fit, CLPM.3.fit) #compare the fit of the RICLPM and CLPM
```


#IWB <-> AQoL 


```{r WBIS PQoL UNCONSTRAINED, eval = F}

RICLPM.4a <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4
  

   # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.4a.fit <- lavaan(RICLPM.4a, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.4a.fit, standardized = T, fit.measures = TRUE)

```


```{r WBIS AQoL constrained, eval = F}

RICLPM.4b <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4
  
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.4b.fit <- lavaan(RICLPM.4b, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.4b.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

anova(RICLPM.4a.fit, RICLPM.4b.fit) #compare the fit of the constrained and unconstrained models

```

```{r WBIS AQoL CLPM, eval = F}

CLPM_4 <- '
  # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
  RIy =~ 1*AQoL_MSD_MEAN_T2 + 1*AQoL_MSD_MEAN_T3 + 1*AQoL_MSD_MEAN_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*AQoL_MSD_MEAN_T2
  wy3 =~ 1*AQoL_MSD_MEAN_T3
  wy4 =~ 1*AQoL_MSD_MEAN_T4

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ wx2 + wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ wx2 + wy2
  wx4 ~ wx3 + wy3
  wy4 ~ wx3 + wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ 0*RIx
  RIy ~~ 0*RIy
  RIx ~~ 0*RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
CLPM.4.fit <- lavaan(CLPM_4, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(CLPM.4.fit, standardized = T, fit.measures = TRUE)


anova(RICLPM.4a.fit, CLPM.4.fit) #compare the fit of the RICLPM and CLPM
```

#RI-CLPMs including covariates 

##standardised with covariates 
- use 'ml.x' for missing data, because 'ML' will delete any cases with missing data for covariates. ml.x will retain cases with missing data for covariates. 
- when including covariates in RI-CLPMs, regress the random intercepts onto all of the covariates (other options for including time invariant predictors are discussed in Mulder & Hamaker (2020))

```{r EDS WBIS RICLPM constrained Z covariates, eval = F}

RICLPM_1z.covariates <- '
  # Create between components (random intercepts)
  RIx =~ 1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*ZWBIS_M_T2 + 1*ZWBIS_M_T3 + 1*ZWBIS_M_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZWBIS_M_T2
  wy3 =~ 1*ZWBIS_M_T3
  wy4 =~ 1*ZWBIS_M_T4
  
    # Regression of random intercepts on covariates
  RIx + RIy ~  Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + ZAge_T2 + ZBMI_T1 + ZSES  # Constrained over time. 

  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1z.covariates.fit <- lavaan(RICLPM_1z.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.1z.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```



```{r WBIS AQoL constrained Z covariates, eval = F}

RICLPM.4z.covariates <- '
  # Create between components (random intercepts)
  RIx =~1*1*ZWBIS_M_T2 + 1*1*ZWBIS_M_T3 + 1*1*ZWBIS_M_T4
  RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*1*ZWBIS_M_T2
  wx3 =~ 1*1*ZWBIS_M_T3
  wx4 =~ 1*1*ZWBIS_M_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ ZSES + ZBMI_T1 + Race_Asian  + Race_White + Race_Hispanic + Race_Black + Race_multi + ZAge_T2 # Constrained over time. 
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.4z.covariates.fit <- lavaan(RICLPM.4z.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.4z.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r WBIS BMI constrained Z covariates, eval = F}

RICLPM.5z.covariates <- '
  # Create between components (random intercepts)

  RIx =~ 1*ZBMI_T2 + 1*ZBMI_T3 + 1*ZBMI_T4
    RIy =~1*ZWBIS_M_T2 + 1*ZWBIS_M_T3 + 1*ZWBIS_M_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*ZBMI_T2
  wx3 =~ 1*ZBMI_T3
  wx4 =~ 1*ZBMI_T4
 
  wy2 =~ 1*ZWBIS_M_T2
  wy3 =~ 1*ZWBIS_M_T3
  wy4 =~ 1*ZWBIS_M_T4
  

  
     # Regression of random intercepts on covariates
  RIx + RIy ~ ZSES + Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + ZAge_T2 # Constrained over time. 
  
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5z.covariates.fit <- lavaan(RICLPM.5z.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.5z.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r EDS AQoL constrained Z covariates, eval = F}

RICLPM_3z.covariates <- '
  # Create between components (random intercepts)
  RIx =~1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4
  RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ ZSES + ZBMI_T1 +Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + ZAge_T2 # Constrained over time. 
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.3z.covariates.fit <- lavaan(RICLPM_3z.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.3z.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r BMI EDS constrained Z covariates, eval = F}

RICLPM_2z.covariates <- '
  # Create between components (random intercepts)
  RIx =~1*ZEDS_T2 + 1*ZEDS_T3 + 1*ZEDS_T4
  RIy =~ 1*ZBMI_T2 + 1*ZBMI_T3 + 1*ZBMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*ZEDS_T2
  wx3 =~ 1*ZEDS_T3
  wx4 =~ 1*ZEDS_T4
  
  wy2 =~ 1*ZBMI_T2
  wy3 =~ 1*ZBMI_T3
  wy4 =~ 1*ZBMI_T4
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ ZSES + Race_Asian +  Race_White + Race_Hispanic + Race_Black + Race_multi + ZAge_T2 # Constrained over time. 

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2z.covariates.fit <- lavaan(RICLPM_2z.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2z.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```


##unstandardized with covariates


```{r EDS WBIS RICLPM constrained covariates, eval = F}

RICLPM_1.covariates <- '
   RIx =~ 1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4   #the 1* constrains the factor loadings to 1 
  RIy =~ 1*WBIS_M_MEAN_T2+ 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 
  
  # Create within-person centered variables (i.e., the within-person portion of the observed scores) 
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  
  
    # Regression of random intercepts on covariates
  RIx + RIy ~  Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + Age_T2 + BMI_T1 + SES_T1  # Constrained over time. 

  

  # Estimate the lagged effects between the within-person centered variables. (cross-lagged and auto-regressive effects)
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2       #i.e., we arent predetermining their value (e.g., factor loading of 1), we are just letting them be equal over time
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
  

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx    #variance
  RIy ~~ RIy
  RIx ~~ RIy    #covariance

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.1.covariates.fit <- lavaan(RICLPM_1.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.1.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```



```{r WBIS AQoL constrained covariates, eval = F}

RICLPM.4.covariates <- '
   # Create between components (random intercepts)
  RIx =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4
 RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*WBIS_M_MEAN_T2
  wx3 =~ 1*WBIS_M_MEAN_T3
  wx4 =~ 1*WBIS_M_MEAN_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ SES_T1 + BMI_T1 + Race_Asian  + Race_White + Race_Hispanic + Race_Black + Race_multi + Age_T2 # Constrained over time. 
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.4.covariates.fit <- lavaan(RICLPM.4.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.4.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r WBIS BMI constrained covariates, eval = F}

RICLPM.5.covariates <- '
  # Create between components (random intercepts)
  
    RIx =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4

 RIy =~1*WBIS_M_MEAN_T2 + 1*WBIS_M_MEAN_T3 + 1*WBIS_M_MEAN_T4

 
  
  # Create within-person centered variables
 
   wx2 =~ 1*BMI_T2
  wx3 =~ 1*BMI_T3
  wx4 =~ 1*BMI_T4
 
 
  wy2 =~ 1*WBIS_M_MEAN_T2
  wy3 =~ 1*WBIS_M_MEAN_T3
  wy4 =~ 1*WBIS_M_MEAN_T4
  


  
     # Regression of random intercepts on covariates
  RIx + RIy ~ SES_T1 + Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + Age_T2 # Constrained over time. 
  
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.5.covariates.fit <- lavaan(RICLPM.5.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.5.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r EDS AQoL constrained covariates, eval = F}

RICLPM_3.covariates <- '
   # Create between components (random intercepts)
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
   RIy =~ 1*ZAQoL_T2 + 1*ZAQoL_T3 + 1*ZAQoL_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*ZAQoL_T2
  wy3 =~ 1*ZAQoL_T3
  wy4 =~ 1*ZAQoL_T4
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ SES_T1 + BMI_T1 + Race_Asian + Race_White + Race_Hispanic + Race_Black + Race_multi + Age_T2 # Constrained over time. 
  

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.3.covariates.fit <- lavaan(RICLPM_3.covariates, data = merged_final, missing = 'ml.x', meanstructure = T, int.ov.free = T) 
summary(RICLPM.3.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)


```

```{r BMI EDS constrained covariates, eval = F}

RICLPM_2.covariates <- '
  # Create between components (random intercepts)
 
  RIx =~1*EDS_bodyweight_MEAN_T2 + 1*EDS_bodyweight_MEAN_T3 + 1*EDS_bodyweight_MEAN_T4
  RIy =~ 1*BMI_T2 + 1*BMI_T3 + 1*BMI_T4
 
  
  # Create within-person centered variables
 
  wx2 =~ 1*EDS_bodyweight_MEAN_T2
  wx3 =~ 1*EDS_bodyweight_MEAN_T3
  wx4 =~ 1*EDS_bodyweight_MEAN_T4
  
  wy2 =~ 1*BMI_T2
  wy3 =~ 1*BMI_T3
  wy4 =~ 1*BMI_T4
  
     # Regression of random intercepts on covariates
  RIx + RIy ~ SES_T1 + Race_Asian +  Race_White + Race_Hispanic + Race_Black + Race_multi + Age_T2 # Constrained over time. 

  # Estimate the lagged effects between the within-person centered variables.
  wx3 ~ a*wx2 + b*wy2      #pre-multiplication (*) with the same label constrains these paths to be equal over time 
  wy3 ~ c*wx2 + d*wy2
  wx4 ~ a*wx3 + b*wy3
  wy4 ~ c*wx3 + d*wy3
 

  # Estimate the covariance between the within-person centered variables at the first wave. 
  wx2 ~~ wy2 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations).
  wx3 ~~ wy3
  wx4 ~~ wy4

  
  # Estimate the variance and covariance of the random intercepts. 
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx2 ~~ wx2 # Variances
  wy2 ~~ wy2 
  wx3 ~~ wx3 # Residual variances
  wy3 ~~ wy3 
  wx4 ~~ wx4 
  wy4 ~~ wy4 
 
'
RICLPM.2.covariates.fit <- lavaan(RICLPM_2.covariates, data = merged_final, missing = 'ML', meanstructure = T, int.ov.free = T) 
summary(RICLPM.2.covariates.fit, standardized = T, fit.measures = TRUE, ci = TRUE)

```



