---
title: "Austen & Griffiths (2021) code for data importation and cleaning"
output: html_notebook
---

Please note: this code commences following de-identification of data, as well as calculation of race variables in SPSS. The syntax we used to calculate our race frequency vars is also available on our OSF page. Please contact Emma Austen (eausten@student.unimelb.edu.au) with any queries or suggestions! 

For those interested in running models on our composite vars (i.e., our finalised dataset), please see our R notebook for our analysis code. This code is predominantly for data cleaning, as well as calculating Cronbach's alphas and missing data analyses for each timepoint. By the end of this notebook, the data should look identical to the "Final_merged_clean.csv" dataset on the OSF

Throughout this code, variable names may not correspond with "timepoint" named in the dataset (e.g., there are _T2 variables in the T1 dataset/object): this is because the timepoint indicated in the variable name (denoted as _T1 or T2 or T3) takes into account the first demographic wave of Gay Bodies Worldwide (denoted by _T1 in all of the dataset variables, and T0 in the dataset/object var names). For the purpose of this paper, we renamed the timepoints of Gay Bodies Worldwide: Time 1 = Time 0 for this paper, Time 2 in variable names = Time 1 in this paper, Time 3 in variable names= Time 2 in this paper, and Time 4 in variable names = Time 3 in this paper. Apologies for any confusion :-) 

#load packages
```{r load packages}

library(tidyverse) #for dplyr, ggplot, etc.
library(haven) 
library(digest) #for producing hash IDs
library(psych) #for looking at descriptives 
library(lubridate) #doing date things
library(pastecs) #for descriptives table
library(sjlabelled)
library(anytime) #also for doing date things, when lubridate functions don't work


```


#Import raw, deidentified datasets 

```{r}

T0_raw <- read.csv("T0_demographics_raw.csv")

T1_raw <- read.csv("T1_raw.csv")

T2_raw <- read.csv("T2_raw.csv")

T3_raw <- read.csv("T3_raw.csv")

```

#T0: demographic wave - calculating some variables and filtering to relevant demographic vars for analyses 
```{r demographics}

#BMI 

  ##height vars

  #because we sum across columns to create a combined height variable, we should assign missing values as 0 
T0_raw$Height_FeetInches_1_New [is.na(T0_raw$Height_FeetInches_1_New)] = 0
T0_raw$Height_FeetInches_2_New[is.na(T0_raw$Height_FeetInches_2_New)] = 0
T0_raw$Height_Centimetres_1_New[is.na(T0_raw$Height_Centimetres_1_New)] = 0
    #can use replace_na() in mutate instead of doing this lengthy version (see weight var calcs)


T0_raw<- T0_raw %>% #need to assign to an object otherwise the transformations won't "stick"
  mutate(Height_Centimetres_1_New = as.numeric(Height_Centimetres_1_New),
         Height_FeetInches_1_New = as.numeric(Height_FeetInches_1_New), 
         Height_FeetInches_2_New = as.numeric(Height_FeetInches_2_New)) %>% 
  mutate(Height_FeetInches_convert=(Height_FeetInches_1_New*30.48) + (Height_FeetInches_2_New * 2.54)) %>%  #convert ft inches to cm
  mutate(Height_combined = (Height_Centimetres_1_New + Height_FeetInches_convert)) %>%  #overall height variable (ie one metric for BMI calc)
  mutate(Height_combined = na_if(Height_combined, 0)) %>%  #then we convert the 0's back to missing before we calc BMI
  mutate(Height_meters = (Height_combined/100))


  ##weight vars and final BMI calculation 

T0_raw <- T0_raw %>%  
  mutate(Weight_StonesPounds_1_New = replace_na(Weight_StonesPounds_1_New, 0)) %>% 
  mutate(Weight_StonesPounds_convert = (Weight_StonesPounds_1_New * 6.35) + (Weight_StonesPounds_2_New/2.205)) %>% 
  mutate(Weight_Pounds_convert = (Weight_Pounds_1_New/2.205)) %>% 
  mutate(Weight_StonesPounds_convert = replace_na(Weight_StonesPounds_convert, 0), 
         Weight_Pounds_convert = replace_na(Weight_Pounds_convert, 0), 
         Weight_kilograms_1_New = replace_na(Weight_kilograms_1_New, 0), 
         Weight_combined = (Weight_kilograms_1_New + Weight_StonesPounds_convert + Weight_Pounds_convert)) %>% 
  mutate(Weight_combined_T1 = na_if(Weight_combined, 0)) %>%  
  mutate(BMI_T1 =  Weight_combined_T1/ (Height_meters * Height_meters)) %>%  #BMI 
  mutate(Day = 1, #set day of birth to 1st of month
         Birthday = make_date(Year, Month, Day)) 
  
```

##filter

We won't need the weight stigma data from this wave, just the demographics 

```{r}

T0_raw <-  mutate(rename(T0_raw, Likelihood_T1 = Likelihood, 
                SES_T1 = SES_ladder,
                Duration_T1 = Duration__in_seconds, 
                EndDate_T1 = EndDate,
                StartDate_T1 = StartDate, 
                Progress_T1 = Progress,  
                Country_T1 = Country, 
                Sex_identity_T1 = Sex_identity, 
                Sex_attraction_T1 = Sex_Attraction, 
                Sex_experiences_T1 = Sex_Experiences, 
                Gender_T1 = Gender, 
                Gender_assigned_T1 = Gender_assigned,
                Height_meters_T1 = Height_meters))
  
T0_clean_unmerged <-T0_raw %>% 
  select(ID:Progress_T1, EndDate_T1, Country_T1, Gender_T1:Sex_identity_T1, Sex_attraction_T1, Sex_experiences_T1, SES_T1, Likelihood_T1:Race_multi, Height_meters_T1, BMI_T1, Birthday) %>% 
  mutate(Wave_1_complete = 1) #this complete = 1 variable is to help identify who participated in all waves versus dropped out of at least one 

```

#T1


##investigate duplicate cases

- extra cases (n = 12) seem to be rows with "NA" values for ID
- filtering these cases to have a look at them, just looks like blank rows that have been inserted upon merging. Therefore, filter out 

```{r duplicates}

ID_obs <- T1_raw %>% count(ID)
#looking at potential duplicate IDs 

ID_check <- T1_raw %>% filter(ID %in% c(NA))
#look at NA rows 

T1_raw <- T1_raw %>% 
  filter(!ID %in% c(NA)) #filter to IDs that are not NA, removes 12 obs, so this works!
```


##filter T2 cases out 

- some T2 participants completed the T1 survey - so, we separate out these participants and merge them with the T2 file later 
- filters out n = 219 
- initial N (i.e., prior to cleaning - removing duplicates, progress <10, etc.) for T2 = 2382

```{r}

T1_raw$StartDate
#date is formatted D/M/Y --> use below code to change to Y-M-D

T1_raw$StartDate <- anydate(T1_raw$StartDate) 
                            #converts this var into a readable date format that we can use to filter cases 
                            #don't have to do this every time, but cleaning in SPSS made the date variable funny 

T2_extras <- T1_raw %>% 
  filter(StartDate > as.Date("2020-01-01")) #filters out the cases that are part of T2 collection 


T1_raw<- T1_raw %>%  
  filter(StartDate <= as.Date("2020-01-01"))  #make sure the way you specify the date is in the same order/format
                                              #as the dates in the variable (e.g., Y/M/D vs D/M/Y)

```

## Calculate scale scores and weight vars for BMI to be calculated in final merge

```{r}

#weight vars
T1_raw <- T1_raw %>%  
  mutate(Weight_StonesPounds_1_New = replace_na(Weight_StonesPounds_1_New, 0)) %>% 
  mutate(Weight_StonesPounds_convert = (Weight_StonesPounds_1_New * 6.35) + (Weight_StonesPounds_2_New/2.205)) %>% 
  mutate(Weight_Pounds_convert = (Weight_Pounds_1_New/2.205)) %>% 
  mutate(Weight_StonesPounds_convert = replace_na(Weight_StonesPounds_convert, 0), 
         Weight_Pounds_convert = replace_na(Weight_Pounds_convert, 0), 
         Weight_kilograms_1_New = replace_na(Weight_kilograms_1_New, 0), 
         Weight_combined_T2 = (Weight_kilograms_1_New + Weight_StonesPounds_convert + Weight_Pounds_convert)) %>% 
  mutate(Weight_combined_T2 = na_if(Weight_combined_T2, 0)) 

#reverse code items and calculate composite (mean or total) scale scores

T1_raw <-  mutate(rename(T1_raw, 
                                            WBIS_M_1_r = WBISM_1_r, WBIS_M_2 = WBISM_2,
                                            WBIS_M_3 = WBISM_3, WBIS_M_4 = WBISM_4, 
                                            WBIS_M_5= WBISM_5, WBIS_M_6= WBISM_6, 
                                            WBIS_M_7 = WBISM_7, WBIS_M_8= WBISM_8,
                                            WBIS_M_9_r = WBISM_9_r, WBIS_M_10 = WBISM_10,
                                            WBIS_M_11 = WBISM_11)) 

T1_raw <- T1_raw %>%
  mutate(WBIS_M_1r = 7 - WBIS_M_1_r,   #reverse scoring 
       WBIS_M_9r = 7 - WBIS_M_9_r, 
       WeightBias_1r = 7 - WeightBias_1, 
       WeightBias_2r = 7 - WeightBias_2,
       WeightBias_3r = 7 - WeightBias_3, 
       WeightBias_4r = 7 - WeightBias_4, 
       WeightBias_5r = 7 - WeightBias_5, 
       WeightBias_6r = 7 - WeightBias_6, 
       WeightBias_8r = 7 - WeightBias_8, 
       WeightBias_14r = 7 - WeightBias_14,
      Body_dissat_M_7r = 5 - Body_dissat_M_7_r) 


T1_raw <- T1_raw %>% 
    mutate(EDS_bodyweight_MEAN_T2 = rowMeans(select(., EDS_bodyweight_1:EDS_bodyweight_9)),#EDS = mean score 
            WBIS_M_MEAN_T2 = rowMeans(select(., c(WBIS_M_2:WBIS_M_8, WBIS_M_10, WBIS_M_11,
                                                  WBIS_M_1r, WBIS_M_9r))), #WBIS-M = mean score
            WeightBias_MEAN_T2 = rowMeans(select(., c(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   #UMB-F = mean score
                                                 WeightBias_9_r:WeightBias_13_r, 
                                                 WeightBias_15_r:WeightBias_20_r))),
            AQoL_MSD_TOTAL_T2 = rowSums(select(., QoL_1_Psych_C1:QoL_35_MH5)), #AQoL = total score
           AQoL_MSD_MEAN_T2 = rowMeans(select(., QoL_1_Psych_C1:QoL_35_MH5)), #AQoL mean score 
           Body_dissat_MEAN_T2 = rowMeans(select(., c(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
                                                      Body_dissat_BF_1:Body_dissat_BF_5)))) #body dissat = mean score 


T1_final <-    #renaming variables here to distinguish T1, T2, etc. 
  mutate(rename(T1_raw, Duration_T2 = Durationinseconds,
                StartDate_T2 = StartDate, 
                EndDate_T2 = EndDate,
                Progress_T2 = Progress, 
                SES_T2 = SES_ladder, 
                Country_T2 = Country, 
                Sex_identity_T2 = Sex_identity, 
                Sex_attraction_T2 = Sex_Attraction, 
                Sex_experiences_T2 = Sex_Experiences, 
                Likelihood_T2 = Likelihood))

```


##Clean
- initial sample: N = 2382
- participants who identified as heterosexual (n = 2)
- those who did not proceed following the consent page/completed less than 10% of the survey completed (n = 83)
- duplicate IDs (n = 7)
- final sample N = 2271

```{r}
T1_final <- T1_final %>% 
  dplyr::filter(Progress_T2 >= 10, Sex_identity_T2 != '4', ID != "385f34bb1bd82e704248ce485e2c6b27") 
    #the ID here did not consent at consent_check (using argument consent_check != 0 didn't work)



ID_obs <- T1_final %>% count(ID)
#looking at potential duplicate IDs 

ID_check <- T1_final %>% filter(ID %in% c("125e93c884feda7f45617e7d57c7bfc0", "13018f882364f9d96e08151d58e5eec8", "1706525c5bdce570840ca2d31927660d", "68138c82917f96952c0aeba9e30921a0",
"6ae31aef820e81db5c94fc90280fc6c1", "75068bcc22da8f4a6ea05ade5a18cc2b", "	a4a53ec0bbe87ede4dad850f3154f2ba")) 

#look at duplicate rows
T1_final <- distinct(T1_final, ID, .keep_all = TRUE) #removes duplicated ID rows

```


##Missing data analysis 
- Missing item level data ranged from 3.1 to 7.1% (M = 6.3%)
- Non-parametric alternative MCAR test revealed no evidence to reject null hypothesis that data was missing at random (p >.05)
``` {r}
library(MissMech)
library(finalfit)

T1_missing <- T1_final %>%  
  dplyr::select(EDS_bodyweight_1:WeightBias_20_r, Weight_combined_T2) %>%   
        ff_glimpse()

T1_missing_check <- T1_final[["Continuous"]][["missing_percent"]] #inspecting specific elements of missing data check, assigning to its own object 

T1_missing_check <- as.numeric(T1_final) #transform to numeric var so we can run descriptives (e.g., M, range) 

describe(T1_missing_check) #returns descriptives on missing percentage 


#inspect patterns of missingness - MCAR? 
T1_MCAR <- T1_final %>%  
  dplyr::select(WBIS_M_1_r:WBIS_M_11, 
         Body_dissat_M_1:Body_dissat_BF_5,QoL_1_Psych_C1:QoL_35_MH5,
         EDS_bodyweight_1:EDS_bodyweight_9, WeightBias_1:WeightBias_9_r)

TestMCARNormality(T1_MCAR)
```

##Cronbach's alphas

- EDS = 0.92 (CI: 0.92, 0.93)
- WBIS-M = 0.94 (0.93, 0.94)
- MBAS-R = 0.88 (0.87, 0.89)
- AQoL-8D = 0.95
- UMB-F = 0.90

```{r cronbach's alpha}

#EDS
T1_final %>% 
  select(EDS_bodyweight_1:EDS_bodyweight_9) %>% 
  alpha()

#WBIS 

T1_final %>% 
  select(WBIS_M_2:WBIS_M_8, WBIS_M_9r, WBIS_M_1r, WBIS_M_10:WBIS_M_11) %>% 
  alpha()

#MBAS-R 

T1_final %>% 
  select(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
        Body_dissat_BF_1:Body_dissat_BF_5) %>% 
  alpha()


#UMB-F

T1_final %>% 
  select(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   
         WeightBias_9_r:WeightBias_13_r, 
         WeightBias_15_r:WeightBias_20_r) %>% 
  alpha()

#AQoL

 T1_final %>% 
  select(QoL_1_Psych_C1:QoL_35_MH5) %>% 
  alpha()

```


##Filter to vars used for analyses 

```{r finalise dataset}

T1_for_merging <- T1_final %>% 
select(ID, StartDate_T2:Duration_T2, Sex_identity_T2, Sex_attraction_T2, Sex_experiences_T2, SES_T2, Country_T2, 
       Weight_combined_T2, EDS_bodyweight_MEAN_T2:Body_dissat_MEAN_T2) %>% 
  mutate(Wave_2_complete = 1)
```


#T2

##investigate duplicate cases

sample size looks a bit off so look if there are duplicates 
- extra cases (n = 4) seem to be rows with "NA" values for ID
- filtering these cases to have a look at them, just looks like blank rows that have been inserted upon merging. Therefore, filter out 

```{r duplicates}

ID_obs <- T2_raw %>% count(ID)
#looking at potential duplicate IDs 

ID_check <- T2_raw %>% filter(ID %in% c(NA))
#look at NA rows 

T2_merged_clean <- T2_raw %>% 
  filter(!ID %in% c(NA))
```


##add extra data from W2
- extras n = 219
```{r}

T2_merged_clean <- rbind(T2_merged_clean, T2_extras)

#creates some duplicates, so remove those 

T2_merged_clean <- distinct(T2_merged_clean, ID, .keep_all = TRUE) #removes duplicated ID rows

```

## Calculate scale scores and weight vars for BMI to be calculated in final merge

```{r}

#weight vars
T2_merged_clean <- T2_merged_clean %>%  
  mutate(Weight_StonesPounds_1_New = replace_na(Weight_StonesPounds_1_New, 0)) %>% 
  mutate(Weight_StonesPounds_convert = (Weight_StonesPounds_1_New * 6.35) + (Weight_StonesPounds_2_New/2.205)) %>% 
  mutate(Weight_Pounds_convert = (Weight_Pounds_1_New/2.205)) %>% 
  mutate(Weight_StonesPounds_convert = replace_na(Weight_StonesPounds_convert, 0), 
         Weight_Pounds_convert = replace_na(Weight_Pounds_convert, 0), 
         Weight_kilograms_1_New = replace_na(Weight_kilograms_1_New, 0), 
         Weight_combined_T3 = (Weight_kilograms_1_New + Weight_StonesPounds_convert + Weight_Pounds_convert)) %>% 
  mutate(Weight_combined_T3 = na_if(Weight_combined_T3, 0)) 

#reverse code items and calculate composite (mean or total) scale scores

T2_merged_clean <-  mutate(rename(T2_merged_clean, 
                                            WBIS_M_1_r = WBISM_1_r, WBIS_M_2 = WBISM_2,
                                            WBIS_M_3 = WBISM_3, WBIS_M_4 = WBISM_4, 
                                            WBIS_M_5= WBISM_5, WBIS_M_6= WBISM_6, 
                                            WBIS_M_7 = WBISM_7, WBIS_M_8= WBISM_8,
                                            WBIS_M_9_r = WBISM_9_r, WBIS_M_10 = WBISM_10,
                                            WBIS_M_11 = WBISM_11)) 

T2_merged_clean <- T2_merged_clean %>%
  mutate(WBIS_M_1r = 7 - WBIS_M_1_r,   #reverse scoring 
       WBIS_M_9r = 7 - WBIS_M_9_r, 
       WeightBias_1r = 7 - WeightBias_1, 
       WeightBias_2r = 7 - WeightBias_2,
       WeightBias_3r = 7 - WeightBias_3, 
       WeightBias_4r = 7 - WeightBias_4, 
       WeightBias_5r = 7 - WeightBias_5, 
       WeightBias_6r = 7 - WeightBias_6, 
       WeightBias_8r = 7 - WeightBias_8, 
       WeightBias_14r = 7 - WeightBias_14,
      Body_dissat_M_7r = 5 - Body_dissat_M_7_r) 


T2_merged_clean <- T2_merged_clean %>% 
    mutate(EDS_bodyweight_MEAN_T3 = rowMeans(select(., EDS_bodyweight_1:EDS_bodyweight_9)),#EDS = mean score 
            WBIS_M_MEAN_T3 = rowMeans(select(., c(WBIS_M_2:WBIS_M_8, WBIS_M_10, WBIS_M_11,
                                                  WBIS_M_1r, WBIS_M_9r))), #WBIS-M = mean score
            WeightBias_MEAN_T3 = rowMeans(select(., c(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   #UMB-F = mean score
                                                 WeightBias_9_r:WeightBias_13_r, 
                                                 WeightBias_15_r:WeightBias_20_r))),
            AQoL_MSD_TOTAL_T3 = rowSums(select(., QoL_1_Psych_C1:QoL_35_MH5)), #AQoL = total score
           AQoL_MSD_MEAN_T3 = rowMeans(select(., QoL_1_Psych_C1:QoL_35_MH5)), #AQoL mean score 
           Body_dissat_MEAN_T3 = rowMeans(select(., c(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
                                                      Body_dissat_BF_1:Body_dissat_BF_5)))) #body dissat = mean score 


T2_final <-   #renaming variables here to distinguish T1, T2, etc. 
  mutate(rename(T2_merged_clean, Duration_T3 = Durationinseconds,
                StartDate_T3 = StartDate, 
                EndDate_T3 = EndDate,
                Progress_T3 = Progress, 
                SES_T3 = SES_ladder, 
                Country_T3 = Country, 
                Sex_identity_T3 = Sex_identity, 
                Sex_attraction_T3 = Sex_Attraction, 
                Sex_experiences_T3 = Sex_Experiences, 
                Likelihood_T3 = Likelihood))

```


## Clean
- initial sample: N = 2008
- participants who identified as heterosexual (n = 3)
- those who did not proceed following the consent page/completed less than 10% of the survey completed (n = 59)
- final sample N = 1936

```{r}
T2_final_clean <- T2_final %>% 
  filter(Progress_T3 >= 10, Sex_identity_T3 != '4')

T2_final_clean<-T2_final_clean[!(T2_final_clean$ID=="385f34bb1bd82e704248ce485e2c6b27" | T2_final_clean$ID=="4dcad14830cb5e7ffdb16bcbd5a35c33"),] 
    #this is a workaround solution as R wouldn't let me exclude cases where Consent_check = 0

```

##Missing data analysis 
- Missing item level data ranged from 3.4 to 6.0% (M = 5.1%)
- Non-parametric alternative MCAR test revealed no evidence to reject null hypothesis that data was missing at random (p >.05)
``` {r}
library(MissMech)
library(finalfit)

T2_missing <- T2_final_clean %>%  
  dplyr::select(EDS_bodyweight_1:WeightBias_20_r, Weight_combined_T3) %>%   
        ff_glimpse()

T2_missing_check <- T2_missing[["Continuous"]][["missing_percent"]] #inspecting specific elements of missing data check, assigning to its own object 

T2_missing_check <- as.numeric(T2_missing_check) #transform to numeric var so we can run descriptives (e.g., M, range) 

describe(T2_missing_check) #returns descriptives on missing percentage 


#inspect patterns of missingness - MCAR? 
T2_MCAR <- T2_final_clean %>%  
  dplyr::select(WBIS_M_1_r:WBIS_M_11, 
         Body_dissat_M_1:Body_dissat_BF_5,QoL_1_Psych_C1:QoL_35_MH5,
         EDS_bodyweight_1:EDS_bodyweight_9, WeightBias_1:WeightBias_9_r)

TestMCARNormality(T2_MCAR)
```


##Cronbach's alphas

- EDS = 0.92 (CI: 0.92, 0.93)
- WBIS-M = 0.94 (0.93, 0.94)
- MBAS-R = 0.89 (0.88, 0.89)
- AQoL-8D = 0.95
- UMB-F = 0.90

```{r cronbach's alpha}

#EDS
T2_final_clean %>% 
  select(EDS_bodyweight_1:EDS_bodyweight_9) %>% 
  alpha()

#WBIS 

T2_final_clean %>% 
  select(WBIS_M_2:WBIS_M_8, WBIS_M_9r, WBIS_M_1r, WBIS_M_10:WBIS_M_11) %>% 
  alpha()

#MBAS-R 

T2_final_clean %>% 
  select(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
        Body_dissat_BF_1:Body_dissat_BF_5) %>% 
  alpha()


#UMB-F

T2_final_clean %>% 
  select(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   
         WeightBias_9_r:WeightBias_13_r, 
         WeightBias_15_r:WeightBias_20_r) %>% 
  alpha()

#AQoL

 T2_final_clean %>% 
  select(QoL_1_Psych_C1:QoL_35_MH5) %>% 
  alpha()

```


##Filter to vars needed for merging 

```{r finalise dataset}
T2_for_merging <- T2_final_clean %>% 
  select(ID, StartDate_T3:Duration_T3, Sex_identity_T3, Sex_attraction_T3, Sex_experiences_T3, SES_T3, Country_T3, 
       Weight_combined_T3, EDS_bodyweight_MEAN_T3:Body_dissat_MEAN_T3)  %>% 
  mutate(Wave_3_complete = 1)

```


#T3


##investigate duplicate cases

sample size looks a bit off so look if there are duplicates 
- extra cases (n = 9) seem to be rows with "NA" values for ID
- filtering these cases to have a look at them, just looks like blank rows that have been inserted upon merging. Therefore, filter out 

```{r duplicates}

ID_obs <- T3_raw %>% count(ID)
#looking at potential duplicate IDs 

T3_merged_clean <- T3_raw  %>% 
  filter(!ID %in% c(NA))

ID_check <- T3_merged_clean %>% filter(ID %in% c("052bf7db23b2359225e84928063d65ec", "16dbf271a8c50ff91be053cb9c244e8a", 
                    "13018f882364f9d96e08151d58e5eec8", "16dbf271a8c50ff91be053cb9c244e8a"))
#look at duplicates


```

## Calculate scale scores and weight vars for BMI to be calculated in final merge

```{r}

#weight vars
T3_merged_clean <- T3_merged_clean %>%  
  mutate(Weight_StonesPounds_1_New = replace_na(Weight_StonesPounds_1_New, 0)) %>% 
  mutate(Weight_StonesPounds_convert = (Weight_StonesPounds_1_New * 6.35) + (Weight_StonesPounds_2_New/2.205)) %>% 
  mutate(Weight_Pounds_convert = (Weight_Pounds_1_New/2.205)) %>% 
  mutate(Weight_StonesPounds_convert = replace_na(Weight_StonesPounds_convert, 0), 
         Weight_Pounds_convert = replace_na(Weight_Pounds_convert, 0), 
         Weight_kilograms_1_New = replace_na(Weight_kilograms_1_New, 0), 
         Weight_combined_T4 = (Weight_kilograms_1_New + Weight_StonesPounds_convert + Weight_Pounds_convert)) %>% 
  mutate(Weight_combined_T4 = na_if(Weight_combined_T4, 0)) 

#reverse code items and calculate composite (mean or total) scale scores

T3_merged_clean <-  mutate(rename(T3_merged_clean, 
                                            WBIS_M_1_r = WBISM_1_r, WBIS_M_2 = WBISM_2,
                                            WBIS_M_3 = WBISM_3, WBIS_M_4 = WBISM_4, 
                                            WBIS_M_5= WBISM_5, WBIS_M_6= WBISM_6, 
                                            WBIS_M_7 = WBISM_7, WBIS_M_8= WBISM_8,
                                            WBIS_M_9_r = WBISM_9_r, WBIS_M_10 = WBISM_10,
                                            WBIS_M_11 = WBISM_11)) 

T3_merged_clean <- T3_merged_clean %>%
  mutate(WBIS_M_1r = 7 - WBIS_M_1_r,   #reverse scoring 
       WBIS_M_9r = 7 - WBIS_M_9_r, 
       WeightBias_1r = 7 - WeightBias_1, 
       WeightBias_2r = 7 - WeightBias_2,
       WeightBias_3r = 7 - WeightBias_3, 
       WeightBias_4r = 7 - WeightBias_4, 
       WeightBias_5r = 7 - WeightBias_5, 
       WeightBias_6r = 7 - WeightBias_6, 
       WeightBias_8r = 7 - WeightBias_8, 
       WeightBias_14r = 7 - WeightBias_14,
      Body_dissat_M_7r = 5 - Body_dissat_M_7_r) 


T3_merged_clean <- T3_merged_clean %>% 
    mutate(EDS_bodyweight_MEAN_T4 = rowMeans(select(., EDS_bodyweight_1:EDS_bodyweight_9)),#EDS = mean score 
            WBIS_M_MEAN_T4 = rowMeans(select(., c(WBIS_M_2:WBIS_M_8, WBIS_M_10, WBIS_M_11,
                                                  WBIS_M_1r, WBIS_M_9r))), #WBIS-M = mean score
            WeightBias_MEAN_T4 = rowMeans(select(., c(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   #UMB-F = mean score
                                                 WeightBias_9_r:WeightBias_13_r, 
                                                 WeightBias_15_r:WeightBias_20_r))),
            AQoL_MSD_TOTAL_T4 = rowSums(select(., QoL_1_Psych_C1:QoL_35_MH5)), #AQoL = total score
           AQoL_MSD_MEAN_T4 = rowMeans(select(., QoL_1_Psych_C1:QoL_35_MH5)),
           Body_dissat_MEAN_T4 = rowMeans(select(., c(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
                                                      Body_dissat_BF_1:Body_dissat_BF_5)))) #body dissat = mean score 


T3_final <-    #renaming variables here to distinguish T1, T2, etc. 
  mutate(rename(T3_merged_clean, Duration_T4 = Durationinseconds,
                StartDate_T4 = StartDate, 
                EndDate_T4 = EndDate,
                Progress_T4 = Progress, 
                SES_T4 = SES_ladder, 
                Country_T4 = Country, 
                Sex_identity_T4 = Sex_identity, 
                Sex_attraction_T4 = Sex_Attraction, 
                Sex_experiences_T4 = Sex_Experiences, 
                Likelihood_T4 = Likelihood))

```


## Clean
- initial sample: N = 1811
- participants who identified as heterosexual (n = 5)
- duplicates (n = 12)
- those who did not proceed following the consent page/completed less than 10% of the survey completed (n = 41)
- final sample N = 1730 

```{r}
T3_final_clean <- T3_final %>% 
  filter(Progress_T4 >= 10, Sex_identity_T4 != '4')


T3_final_clean<-T3_final_clean[!(T3_final_clean$ID=="	39c948759824bdd4de7a3d47eef330e5" | T3_final_clean$ID=="6d8441308d4ad4cbfa14092f597fc1c9"),] 
    #this is a workaround solution as R wouldn't let me exclude cases where Consent_check = 0


T3_final_clean <- distinct(T3_final_clean, ID, .keep_all = TRUE) #removes duplicated ID rows

```

## Missing data analysis 
- Missing item level data ranged from 3.2 to 5.4%  (M = 4.98%)
- Non-parametric alternative MCAR test revealed no evidence to reject null hypothesis that data was missing at random (p >.05)
``` {r}
library(MissMech)
library(finalfit)

T3_missing <- T3_final_clean %>%  
  dplyr::select(EDS_bodyweight_1:WeightBias_20_r, Weight_combined_T4) %>%   
        ff_glimpse()

T3_missing_check <- T3_missing[["Continuous"]][["missing_percent"]] #inspecting specific elements of missing data check, assigning to its own object 

T3_missing_check <- as.numeric(T3_missing_check) #transform to numeric var so we can run descriptives (e.g., M, range) 

describe(T3_missing_check) #returns descriptives on missing percentage 


#inspect patterns of missingness - MCAR? 
T3_MCAR <- T3_final_clean %>%  
  dplyr::select(WBIS_M_1_r:WBIS_M_11, 
         Body_dissat_M_1:Body_dissat_BF_5,QoL_1_Psych_C1:QoL_35_MH5,
         EDS_bodyweight_1:EDS_bodyweight_9, WeightBias_1:WeightBias_9_r)

TestMCARNormality(T3_MCAR)
```



##Cronbach's alphas

- EDS = 0.92 (CI: 0.92, 0.93)
- WBIS-M = 0.94 (0.93, 0.94)
- MBAS-R = 0.89 (0.88, 0.89)
- AQoL-8D = 0.95
- UMB-F = 0.90

```{r cronbach's alpha}

#EDS
T3_final_clean %>% 
  select(EDS_bodyweight_1:EDS_bodyweight_9) %>% 
  alpha()

#WBIS 

T3_final_clean %>% 
  select(WBIS_M_2:WBIS_M_8, WBIS_M_9r, WBIS_M_1r, WBIS_M_10:WBIS_M_11) %>% 
  alpha()

#MBAS-R 

T3_final_clean %>% 
  select(Body_dissat_M_1:Body_dissat_M_6,Body_dissat_M_7r,
        Body_dissat_BF_1:Body_dissat_BF_5) %>% 
  alpha()


#UMB-F

T3_final_clean %>% 
  select(WeightBias_1r:WeightBias_14r, WeightBias_7_r,   
         WeightBias_9_r:WeightBias_13_r, 
         WeightBias_15_r:WeightBias_20_r) %>% 
  alpha()

#AQoL

 T3_final_clean %>% 
  select(QoL_1_Psych_C1:QoL_35_MH5) %>% 
  alpha()

```

##Filter to vars for merging

```{r finalise dataset}
T3_for_merging <- T3_final_clean %>% 
  select(ID, StartDate_T4:Duration_T4, Sex_identity_T4, Sex_attraction_T4, Sex_experiences_T4, SES_T4, Country_T4, 
       Weight_combined_T4, EDS_bodyweight_MEAN_T4:Body_dissat_MEAN_T4) %>% 
  mutate(Wave_4_complete = 1)

```

#merging 

```{r}


merged <- list(T0_for_merging, T1_for_merging, T2_for_merging, T3_for_merging) %>% #use list() to merge more than two dataframes 
  reduce(left_join, by = "ID")

```
 

##filter to only those people enrolled in longitudinal component of GBW
```{r}
#d4cd0dabcf4caa22ad92fab40844c786 = no ID = not enrolled in followup 


merged_2 <- merged %>% 
  filter(!ID %in% c("d4cd0dabcf4caa22ad92fab40844c786"))


```


##Age, BMI calculation for T1, T2, T3
```{r}
merged_2 <- merged_2 %>% 
  mutate(EndDate_T2 = anydate(EndDate_T2),  #Need to convert the date vars to an "unambiguous format" 
         EndDate_T3 = anydate(EndDate_T3),
         EndDate_T4 = anydate(EndDate_T4)) %>% 
  mutate(Age_T2 = as.numeric(difftime(EndDate_T2, Birthday, unit = "days")/365.25), #Age
         Age_T3 = as.numeric(difftime(EndDate_T3, Birthday, unit = "days")/365.25),
         Age_T4 = as.numeric(difftime(EndDate_T4, Birthday, unit = "days")/365.25),
         BMI_T2 = Weight_combined_T2/(Height_meters_T1 * Height_meters_T1), #BMI
         BMI_T3 = Weight_combined_T3/(Height_meters_T1 * Height_meters_T1), 
         BMI_T4 = Weight_combined_T4/(Height_meters_T1 * Height_meters_T1))

```


